{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis, Truth or Just a Dream?}

### 2025-08-05 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

\title{{\fontfamily{ptm}\selectfont My Ideas after Reading Papers}}

@@

% ==============================================================================
\section{Introduction}
    Necoara et al. introduced the definition of quasi strongly convex function (Q-SCNVX), Quadratic Under approximations (QUA), Quadratic Gradient Growth (QGG), Proximal Error Bound (PEB) and, Quadratic Function Growth (QFG). 
    These conditions are relaxation of strong convexity which enables linear convergence rate of first order method, including Nesterov's accelerated variants. 
    In this file, we showed a new perspective of their works. 
    Our goal is to relax their definitions and, to extend the linear convergence results, using completely new ideas and perspective. 
    \par
    \textbf{Notations.}
    Unless specified, our ambient space is $\RR^n$ with Euclidean norm $\Vert \cdot\Vert$.
    Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
    \par
    The following definitions and assumptions are their. 
    % SYMBOL SET FOR THIS CHAPTER ONLY!

@@

    \begin{lemma}[conditions when DSBD behaves like norm squared]

@@

    \subsection{examples for relatively quasi strongly convex functions}

@@

        \begin{assumption}[distance of two sets]

@@

                \item 

@@

@@

        \begin{theorem}[example of restricted QUA]\label{thm:example-rqua}

        \end{theorem}
        \begin{proof}

        \end{proof}
    % ------------------------------------------------------------------------------------------------------------------
    \subsection{theorems useful for convergence analysis of algorithms}
        The proximal gradient inequality and, the Jensen inequality are the most important for deriving convergence rate of first order accelerated method.

>>>>

\title{{\fontfamily{ptm}\selectfont My Ideas after Reading Necoara's Papers}}

@@

% ==============================================================================
\section{Introduction}
    Necoara et al. \cite{necoara_linear_2019}  introduced the definition of quasi strongly convex function (Q-SCNVX), Quadratic Under approximations (QUA), Quadratic Gradient Growth (QGG), Proximal Error Bound (PEB) and, Quadratic Function Growth (QFG). 
    These conditions are relaxation of strong convexity which enables linear convergence rate of first order method, including Nesterov's accelerated variants. 
    In this file, we showed a new perspective of their works. 
    Our goal is to relax their definitions and, to extend the linear convergence results, using completely new ideas and perspective. 
    \par
    \textbf{Notations.}
    Unless specified, our ambient space is $\RR^n$ with Euclidean norm $\Vert \cdot\Vert$.
    Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
    \par
    The following definitions and assumptions are their. 
    % SYMBOL SET FOR THIS CHAPTER ONLY!

@@

    \begin{lemma}[conditions when DSBD behaves like norm squared]\label{lemma:conds-dsbd-like-scnvx}

@@

    \subsection{examples for restricted QUA}

@@

        \begin{assumption}[two sets feasibility problem]\;\label{ass:two-sets-feasibility}\\

@@

                \item $f = (1/2)\dist(x | C)^2$ where $C \subseteq \RR^n$ is a closed and convex set. 
                \item $g = \delta_X(x)$ is the indicator function of $X \subseteq \RR^n$, where $X$ is a closed and convex, nonempty set. 

@@

            Consequently, the set of minimizers is the fixed point set of the alternating projection operators, $X^* = \Fix (\Pi_X \Pi_C)$. 

@@

        We will show that, with additional assumptions, function in the above assumption can satisfy the restricted QUA conditions 
        \begin{theorem}[characterizing restricted QUA]\label{thm:example-rqua}
            Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:two-sets-feasibility}. 
            Then for all $x\in X$ such that $\Pi_{X^*} x\in \mathcal D(x | C)$, it has 
                D_f(x, \Pi_{X^*}x) = \frac{1}{2}\Vert x - \Pi_{X^*} x\Vert^2 = D_f(\Pi_{X^*}x, x). 
            We use Lemma \ref{lemma:conds-dsbd-like-scnvx}, take note that when $z = \Pi_{X^*} x \in \mathcal D(x | C)$, then the lemma says: $D_f(x, \Pi_{X^*}x) = \frac{1}{2}\Vert x - \Pi_{X^*}x\Vert^2= D_f(\Pi_{X^*}x, x)$. 
            The conditions, $\Pi_{X^*}x \in \mathcal D(x | C)$ is not always a given and, it would require some careful thoughts. 
    \subsection{theorems useful for convergence analysis of algorithms}
        The proximal gradient inequality and, the Jensen inequality are the most important for deriving convergence rate of first order accelerated method.

### 2025-08-05 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

            \expect \left \Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert^2 
            &= \expect \left\Vert \expect \tilde \nabla f(x) - \tilde \nabla f(x) \right\Vert^2 
            &= \expect \left\Vert \tilde \nabla f(x)\right\Vert^2 
            - \Vert \nabla f(x)\Vert^2 
            \le (\rho - 1)\Vert \nabla f(x)\Vert^2. 
        The last two equalities, we used the $\expect (X - \expect X)^2 = \expect X^2 - (\expect X)^2$ with $X$ being each of the element of the vector and, the linearity of expectations to apply it individually and them sum it up. 
        The first inequality also uses that equality but $X = \left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert$ instead, and $\expect (X - \expect X)^2 \ge 0$ always. 

>>>>

            \expect \left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert^2
            \Vert \nabla f(x)\Vert^2 
            + \expect \left\Vert\tilde \nabla f(x) \right\Vert^2 
            - 2\expect
            \left\langle 
                \nabla f(x), \tilde \nabla f(x)
            \right\rangle
            \Vert \nabla f(x)\Vert^2 
            + \rho \Vert \nabla f(x)\Vert^2
            - 2\Vert \nabla f(x)\Vert^2
            &= \left(\rho - 1\right) \Vert \nabla f(x)\Vert^2.
        For the first inequality, we used the $\expect (X - \expect X)^2 = \expect X^2 - (\expect X)^2$, and the variance being a non-negative quantity. 
